Models

### 2023-10-02 analysis/models.qmd
Update models.qmd

library(tidyverse)
library(marginaleffects)
library(brms)
library(ggplot2)
library(ggdist)
library(broom)

@@

data <- data |>
  mutate(mrs_90 = fct_relevel(
    mrs_90,
    "0",
    "1",
    "2",
    "3",
    "4",
    "5",
    "6",
  ))

is.ordered(data$mrs_90)

@@

>>>>

library(tidyverse)
library(marginaleffects)
library(brms)
library(ggplot2)
library(ggdist)
library(broom)
library(here)

@@

@@

## Estimate the Causal Effect
